% SPDX-FileCopyrightText: 2025 Vasco Guita <vasco@guita.org>
%
% SPDX-License-Identifier: CC-BY-SA-4.0

\documentclass[11pt,a4paper]{article}
\pagestyle{empty}
\usepackage[margin=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

\begin{document}

\begin{center}
  {\huge \textbf{Vasco Guita}}

  \bigskip

  \href{mailto:vasco@guita.org}{\faAt\ vasco@guita.org}
  \quad
  \faPhone\ +41 78 329 55 20
  \quad
  \faMapMarker* Geneva, Switzerland

  \href{https://www.linkedin.com/in/vasco-guita}{\faLinkedin\ vasco-guita}
  \quad
  \href{https://github.com/vascoguita}{\faGithub\ vascoguita}
  \quad
  \href{https://gitlab.com/vasco.guita}{\faGitlab\ vasco.guita}
\end{center}

\bigskip

\section*{Summary}

\hrule

Software engineer with 7+ years of experience in DevOps, automation, system
administration, and full-stack development. Familiar with CI/CD, cloud
infrastructure, hardware-software integration, and observability.

\section*{Experience}

\hrule

\textbf{Software Engineer --- CERN}
\hfill
Oct 2021 --- Present

Led automation and infrastructure projects, built CI/CD pipelines, developed
software, implemented observability, and contributed to open source
collaboration initiatives.

\begin{itemize}[noitemsep]
  \item Deployed hardware-in-the-loop testing infrastructure using OpenStack and
  S3.
  \item Automated infrastructure with Puppet, Foreman, Terraform, and Ansible.
  \item Developed CI/CD pipelines with GitHub Actions, GitLab CI/CD, and Drone
  CI\@.
  \item Packaged 30+ Linux drivers, libraries, and tools for Debian and RPM
  distributions.
  \item Built Docker images for testing, packaging, and simulation.
  \item Developed large-scale storage services used by \textbf{30,000+ users}
  and provided L3 support.
  \item Distributed tracing with OpenTelemetry, Jaeger, Elasticsearch, and
  Kibana dashboards.
  \item Modernized Open Hardware Repository, migrated
  \textbf{500+ projects and 600+ users}, and developed new website.
\end{itemize}

\textbf{Software Engineer --- MARETEC}
\hfill
Feb 2021 --- Sep 2021

Developed tools for maritime applications, focusing on bathymetry visualization.

\begin{itemize}[noitemsep]
  \item Developed plugin for QGIS using Python and Qt to visualize underwater
  terrain.
\end{itemize}

\textbf{Teaching Assistant --- IST, Universidade de Lisboa}
\hfill
Feb 2019 --- Feb 2021

Lectured Network and Computer Security lab classes for B.Sc.\ and M.Sc.\
students.

\begin{itemize}[noitemsep]
  \item Guided students through exercises and projects in Network and
  Computer Security.
  \item Evaluated projects and assignments, and offered support during
  office hours.
  \item Recognized with the \textbf{\faAward\ Excellence in Teaching Award}.
\end{itemize}

\textbf{System Administrator --- IST, Universidade de Lisboa}
\hfill
Dec 2017 --- Sep 2019

Managed IT infrastructure, supporting students and staff.

\begin{itemize}[noitemsep]
  \item Deployed and maintained Linux infrastructure (20+ servers, 100+ VMs) and
  Windows Domain (30+ machines) using libvirt/QEMU/KVM and Ansible.
  \item Deployed 5 Moodle instances serving 1,000+ users and developed
  plugins.
\end{itemize}

\textbf{Repair Technician --- Worten}
\hfill
Oct 2017 --- Dec 2017

Performed technical repairs and customer support in electronics retail.

\begin{itemize}[noitemsep]
  \item Repaired computers and smartphones.
  \item Provided after-sales support, resolving customer issues and improving
  satisfaction.
\end{itemize}

\section*{Education}

\hrule

\textbf{M.Sc.\ Computer Science and Engineering}
\hfill
Sep 2018 --- Sep 2021

\faUniversity\ IST, Universidade de Lisboa

\begin{itemize}[noitemsep]
  \item Specialization in Cyber-Security and Cyber-physical Systems.
  \item Thesis: Data Recovery for Hardware Security Extensions ---
  \textbf{graded 20/20}.
  \item Erasmus: 1 year at Politechnika Lubelska, Poland.
\end{itemize}

\textbf{B.Sc.\ Computer Science and Engineering}
\hfill
Sep 2015 --- Sep 2018

\faUniversity\ IST, Universidade de Lisboa

\section*{Languages}

\hrule

Portuguese (C2), English (C2), French (B1), German (B1), and Polish (A1).

\section*{Projects and Hobbies}

\hrule

\begin{itemize}[noitemsep]
  \item Self-Hosted Infrastructure: WireGuard, Vaultwarden, and Nextcloud on
  Raspberry Pis.
  \item 3D Modeling and Printing: FreeCAD and Prusa printer.
  \item Polish Choir: Singing in a choir and learning Polish.
  \item Model Rocket: Build and launch R-candy rocket.
  \item Model Airplane: Hawker Hurricane.
  \item Smart TV\@: Orange Pi, recycled laptop screen, and Kodi.
\end{itemize}

\section*{Volunteering}

\hrule

\begin{itemize}[noitemsep]
    \item Théâtre for a Cause, Geneva: sell tickets, drinks, and snacks.
    \item VPN Setup: pfSense VPN between INESC-ID and AMA\@.
    \item Catholic Summer Camp Counselor: organize activities for children.
    \item Karate Instructor at ANAM\@: teach children 5--12 years old.
    \item Tutor: math and Portuguese for children with learning difficulties.
    \item Build and Repair Computers: for hospitalized children and parish.
\end{itemize}

\end{document}
